\chapter{Legislation}

	\section{Precedence}
		\begin{enumerate}
			\item The legislation of this chapter will be superseded by the Theta Chi \gls{ibl}, Theta Chi International Legislation, legislation passed by the Grand Chapter of Theta Chi Fraternity, and the Beta Nu of Theta Chi Local Bylaws.

		\end{enumerate}

	\section{Categories and Duration}
		\begin{enumerate}
			\item Temporary legislation 
			\begin{enumerate}
				\item Will be in effect for one year from the date of enactment specified by the legislation.
				\item Expires one year from the date of passage if the date of enactment is not specified.
				\item At the last meeting of each month, the Vice President will report to the chapter on all temporary legislation which will expire in the following month.
			\end{enumerate}
			\item Permanent legislation
			\begin{enumerate}
				\item Will remain in effect indefinitely, until revoked or amended as specified below.
				\item Will be added to the appropriate appendix by the Vice President.
			\end{enumerate}
			\item Emergency legislation:
			\begin{enumerate}
				\item Can be passed by a vote 50\% of those present and eligible to vote even if \gls{qorm} is not present. %While we normally discourage explicitly stating the type of vote (use of the glossary is preferred), it needed to be in this place so as to avoid having to say "providing quorum is present" everywhere else.
				\item At the next chapter meeting where \gls{qorm} is present, the Vice President will bring the emergency legislation before the chapter as permanent or temporary legislation.
			\end{enumerate}
			\item Executive Edicts
			\label{exec-edict}
			\begin{enumerate}
				\item Must be approved by an \gls{abs-maj} vote of \gls{ec}, which immediately puts the edict into effect as legislation.
				\item Supersede all previous legislation.
				\item At the next chapter meeting at which \gls{qorm} is present, the Vice President will bring the edict before the chapter as permanent or temporary legislation. The chapter must then approve the legislation for the edict to remain in effect. %During the next revision, try to fix all structures like this.
			\end{enumerate}
			\item If the legislation is not proposed as one of the above types, it will be treated as temporary legislation.
		\end{enumerate}

	\section{Passage}
		\begin{enumerate}
			\item All motions for legislation must be submitted in writing to the Secretary at a time decided by the Secretary. This time is not to exceed twelve hours before the next chapter meeting. \label{legislation-time}

			\item Legislation requires a \gls{simp-maj} for passage. 

			\item Only emergency legislation may be passed if \gls{qorm} is not present.

		\end{enumerate}

	\section{Revoking or Amending}
		\begin{enumerate}
			\item The legislation of this chapter may be revoked or amended by a \gls{simp-maj} vote.
			\item No legislation can be revoked or amended if \gls{qorm} is not present.

		\end{enumerate}


