\chapter{Expectations of Brothers}
\label{expectations-bhood}

\section{Code of Conduct}
	\begin{enumerate}
		\item No brother will reveal the secrets of the fraternity to anyone who is not an initiated member of Theta Chi Fraternity.
		\item All brothers will obey all federal, state, and local laws.
		\item All brothers will obey all University regulations, \gls{fipg} guidelines, and \gls{ifc} Constitution and Bylaws.
		\item All brothers will obey the \gls{ibl}.
		\item All brothers will obey the local bylaws and the provisions of the lease on the fraternity house.
		\item All brothers will strive at all times to prevent conflicts and strife within the chapter.
		\item All brothers will, at all times, behave as gentlemen.
		\item All brothers will live by the Law of the Helping Hand.
		\item All brothers will regularly \gls{attend} fraternity events.

	\end{enumerate}

\section{Standards of Brotherhood}
	
	\begin{enumerate}
		\item Financial
			\begin{enumerate}
				\item Brothers will abide by the financial obligations outlined in \hyperref[fin-obligations]{Article VI, \autoref*{fin-obligations}}. 
			\end{enumerate}

		\item Rush
			\begin{enumerate}
				\label{rush-attend-std}
				\item Brothers will \gls{attend} over $\frac{3}{4}$ of all rush events.
                \item The recruitment plan may specify a different fraction.  Such a specification is not to be considered a bylaw amendment, and will apply for one semester only.
				\item As rush is one of the most important times for the chapter, brothers will be on their best behavior.
			\end{enumerate}

		\item Social
			\begin{enumerate}
				\item Brothers will \gls{attend} a majority of \glspl{social} each semester unless they are on \gls{academic-probation}. 
				\item Brothers not on \gls{academic-probation} will be involved in at least one non-greek campus student organization.
			\end{enumerate}

	\item Scholarship
		\begin{enumerate}
			\item Brothers will abide by the scholarship standards described in \hyperref[member-schol-stds]{Article X, \autoref*{member-schol-stds}}. 
		\end{enumerate}
	
	\item Service
		\begin{enumerate}
			\item Brothers will complete the service hours assigned to them by the Philanthropy and Service Chairman.
		\end{enumerate}

	\item Chapter Events
		\begin{enumerate}
			\item When an event is declared an \gls{official-chapter-event} by \gls{ec}, all members must \gls{attend} it unless excused by \gls{ec}. A missed \gls{official-chapter-event} that is not excused will count as a missed chapter meeting.
				\begin{enumerate}
					\item An unexcused mandatory event will count as an unexcused mandatory event.

					\item A brother who has three unexcused mandatory events in a row must be brought up for standards by the Secretary with the possibility of suspension

					\item A brother who has three unexcused mandatory events throughout the semester will be staggard.

					\item A brother who has five unexcused mandatory events throughout the semester will be placed on probation until the end of the semester.

					\item A brother who has seven or more unexcused mandatory events throughout the semester will be brought up for standards by the Secretary with the possibility of suspension.
				\end{enumerate}

			\item Brothers will attend chapter meetings as outlined in \hyperref[attendance]{Article III, \autoref*{attendance}}.
		\end{enumerate}
	
	\item Committees
		\begin{enumerate}
			\item Brothers will be an active member of at least one standing committee and one operational committee as defined in \hyperref[committees]{Article V, \autoref*{committees}}.
            \item Brothers will attend assigned committee meetings as outlined in Article V.G.1.
		\end{enumerate}

	\item Other Standards 
		\begin{enumerate}
			\item Many standards do not occur on this list or in the bylaws and  violations will be considered Conduct Unbecoming a Brother. 
		\end{enumerate}
	\end{enumerate}
