\chapter{Scholarship}


\section{Scholarship Chairman}
	\begin{enumerate}
		\item The Scholarship Chairman will be elected in accordance with \hyperref[elections]{Article V, \autoref*{elections}}.

		\item The Scholarship Chairman is responsible for all the duties outlined in \hyperref[schol-chair-duties]{Article V, Section D, \autoref*{schol-chair-duties}}.

	\end{enumerate}


\section{Member Scholarship}
	\label{member-schol-stds}
	\begin{enumerate}

	\item Scholarship Standards
		\begin{enumerate}
			\item Once per semester, brothers and Candidates will fill out grade release forms.
			\begin{enumerate}
				\item Grade release forms must be filled out prior to the due date for midterm grades.
			\end{enumerate}

			\item Members will be evaluated according to the following criteria:\label{academic-probation}	
			\begin{enumerate}
				\item Any brother with a semester \gls{gpa} less than 3.0 is placed on \gls{academic-watch}.  Any brother with a  \gls{gpa} less than 2.7 is placed on \gls{academic-probation}. Any brother with a \gls{gpa} less than 2.5 is placed on \gls{prob}. Any brother with a  \gls{gpa} less than 2.25 will be brought up for suspension.
				
				\begin{enumerate}
					\item A brother on \gls{academic-watch} is required to make a \gls{grade-imp-plan} with the Scholarship Chairman. This plan will be approved by the Scholarship Chairman, the President, and the brother. Failure to follow the \gls{grade-imp-plan} will result in the brother being brought up for standards.
					\label{academic-watch} 
					
					\item A brother on \gls{academic-probation} will have the same responsibilities as those on \gls{academic-watch}. In addition he is allowed to attend at maximum 3 social events per semester. His responsibilities for rush are reduced to one third of events. This brother will not be allowed to hold a position. \label{officer-eligibility}
					\label{academic-probation} 
					
					\item A brother on \gls{prob} will have the same responsibilities as those on \gls{academic-probation}.  In addition he will also not be obligated to attend any rush events and not be allowed to receive a little.
				\end{enumerate}

				\item A brother shall be automatically suspended if:
				\begin{enumerate}
					\item That brother has a semester \gls{gpa} less than 2.35(up for discussion).
					\item That brother did not have a \gls{gpa} greater than 3.00(up for discussion) the semester before.
				\end{enumerate}
				\item Any brother suspended automatically for failure to meet academic standards shall be reinstated once they submit to the President and Scholarship Chair that he now meets academic standards.
				\begin{enumerate}
					\item Needs to be defined
				\end{enumerate}
				\item A brother shall be automatically brought up to Standards Board if:
				\begin{enumerate}
					\item He has a semester \gls{gpa} less than 2.35(up for discussion).
					\item He has a cumulative \gls{gpa} less than 2.50(up for discussion).
				\end{enumerate}
			\end{enumerate}

		\item If a brother is participating in a program where he does not receive a \gls{gpa} and would be placed on \gls{academic-probation}:
			\begin{enumerate}
				\item He is not placed on \gls{academic-probation}.
				\item The next semester in which he is not participating in such a program, he will be placed on \gls{academic-probation}.
			\end{enumerate}

		\end{enumerate}
	\end{enumerate}


\section{New Member Scholarship}
	\begin{enumerate}
		\item During the New Member program, the Scholarship Chairman will meet with the New Members during a regular New Member meeting to explain the chapter \Gls{schol-program} and answer any questions they have.
		
		\item New Members will be held to the academic standards in \hyperref[member-schol-stds]{Article X, \autoref*{member-schol-stds}}.

		\item Candidates will be required to sign grade releases no later than 14 days of grade releases being made available.

		\begin{enumerate}
			\item Upon receiving a Candidate's \gls{gpa}, and finding it does not meet the requirements stated in X.C.4, the Marshal shall announce this at the next regularly scheduled chapter meeting.
		\end{enumerate}
		
		\item A candidate is eligible for initiation if and only if he achieved higher than a 3.0 GPA in the previous semester, or if he has a cumulative GPA of greater than 2.5.
		
		\begin{enumerate}
			\item First semester freshmen are exempt from this rule.
		\end{enumerate}
		
		\item Any Candidate that is ineligible to be initiated due to academic reasons may and should be encouraged to remain included in the scholarship plan until they can become eligible for initiation.

		\item Any Canidate that is ineligible to be initiated will have the option to remain a Candidate.

		\begin{enumerate}
			\item Should a Candidate remain ineligible in any sunsequent semester, he may remain a Candidate only with an absolute majority vote by the active chapter
		\end{enumerate}

	\end{enumerate}

\section{Privacy}
	\begin{enumerate}
		\item The President, Scholarship Chairman, Alumni Advisor, and Faculty Advisor are permitted to know the \gls{gpa} of each brother.

		\item All brothers can know the names of brothers on academic warning and \gls{academic-probation}.

		\item All brothers can know the names of brothers who cannot hold office due to grades.

		\item All brothers can see a histogram of the members' \gls{gpa} but no names will be given and full individual confidentiality will be ensured.

	\end{enumerate}
