\chapter{Chapter Meetings}

\section{Time}

	\begin{enumerate}
		\item The active chapter will meet once per week while school is in session, as required by \gls{ibl} Section V.7.A. 

		\item The default time for a chapter meeting will be Sunday at 6:30 PM unless legislated otherwise.

	\end{enumerate}

\section{Excuses}

	\begin{enumerate}
		\item Excuses for chapter meetings must be submitted in writing to the
		Secretary prior to the meeting or at a time decided by the Secretary. \label{excuses}

		\item Excuses must be approved by an \gls{abs-maj} vote of \gls{ec}.

		\item Failure to \gls{attend} a chapter meeting without an approved excuse (in accordance with \hyperref[excuses]{Article III, Section B, \autoref*{excuses}}) will count as an unexcused absence.

		\item Missing part, but not all, of a chapter meeting without an approved excuse (in accordance with \hyperref[excuses]{Article III, Section B, \autoref*{excuses}}) will count as $\frac{1}{2}$ of an unexcused absence.

	\end{enumerate}

\section{Absences}
	\label{attendance}

	\begin{enumerate}

		\item A brother who has three unexcused absences in a row, not including those from being late to chapter, must be brought up for standards by the Secretary with the possibility of suspension.

		\item A brother who has three unexcused absences throughout the semester will be \gls{staggard}.

		\item A brother who has five unexcused absences throughout the semester will be placed on \gls{prob} until the end of the semester.

		\item A brother who has seven unexcused absences throughout the semester will be brought up for standards by the Secretary with the possibility of suspension. 

	\end{enumerate}

\section{Rules and Regulations}

	\begin{enumerate}
		\item All officer reports and communications must be submitted in writing to the Secretary prior to a chapter meeting at a time decided by the Secretary. Emergency reports or communications may be given at the discretion of the presiding officer.
		\item No one will leave any chapter meeting unless excused by the presiding officer.

		\item Any member whose conduct is unbecoming of a brother may be asked to leave the meeting by the presiding officer.

		\item The First Guard will determine and enforce proper dress code at chapter meetings. \label{chapter-dress}

		\item At the discretion of the First Guard, entrance to chapter meetings will be conducted according to Ritual.

		\item The Marshal will be allowed to bring New Members into chapter meetings, provided:

			\begin{enumerate}

				\item The chapter has been notified at least one week in advance.

				\item \Gls{ec} does not specify otherwise.

			\end{enumerate}

		\item No guests will be permitted within the house during a chapter meeting or the preparation thereof unless permitted by the chair.
		
        \item There will be no food or drink, with the exception of water in a resealable container, at any chapter meeting.

	\end{enumerate}
