\chapter{Chapter Bylaws}

\section{Bylaws as Pertaining to the International Fraternity}

	\begin{enumerate}
		\item The Bylaws of Beta Nu Chapter of Theta Chi Fraternity are adopted as provided for in the \gls{ibl} of Theta Chi Fraternity (Article V, Section 1).

		\item The bylaws of this chapter will be superseded by the \gls{ibl} of Theta Chi Fraternity.
	\end{enumerate}

\section{Amendments}
\label{bylaw-amendments}
	\begin{enumerate}
		\item All motions for proposed amendments must be submitted in writing to the Secretary at a time decided by the Secretary. This time is not to exceed twelve hours before the chapter meeting at which it is to be voted upon. \label{bylaw-time}

		\item All proposed amendments to these Bylaws will specify in the motion that they are amendments.

		\item A proposed Amendment may not be voted on unless, prior to the vote, it has been brought up at least one chapter meeting and has been available for inspection for at least six days.

		\item A proposed amendment must receive a \gls{super-maj} vote for ratification.

	\end{enumerate}

\section{Suspension}
\label{suspend-bylaws}
	\begin{enumerate}
		\item Portions of the bylaws may be suspended by \gls{super-maj} vote of the chapter.
		\item Motions to suspend a portion of the bylaws must contain:
			\begin{enumerate}
				\item To whom the suspension applies.
				\item The time period during which the suspension applies.
				\item The portion to be suspended.
			\end{enumerate}
		\item The \gls{ec} may issue an Executive Edict by \gls{abs-maj} vote in the case of an emergency.
			\begin{enumerate}
				\item The Executive Edict will be proposed to the chapter at the next chapter meeting with \gls{qorm} by the Vice President.
				\item The Executive Edict must be approved by the chapter by a \gls{super-maj} vote in order for the Executive Edict to remain in effect.
			\end{enumerate}
	\end{enumerate}

\section{Interpretation}
	\label{interpretation}
	\begin{enumerate}
		\item \Gls{ec} will have the power to interpret these Bylaws.

		\item Any interpretations that are made will be added to the appropriate appendix by the Vice President.

		\item Any brother may bring \glspl{grieve}, in writing, to \gls{ec}.

		\begin{enumerate}
			\item A \gls{grieve} submitted to \gls{ec} will only be considered if said \gls{grieve} involves a matter of interpretation of these Bylaws.

			\item All \glspl{grieve} brought to \gls{ec} will at all times be confidential.

			\item The results of the \gls{grieve} will be announced to the chapter at the next chapter meeting.

			\begin{enumerate}
				\item \gls{ec} interpretation is subject to overrule by a \gls{super-maj} vote of the active chapter.

				\begin{enumerate}
					\item Voting to overrule an \gls{ec} interpretation of these Bylaws will be done by \gls{balloting}.
				\end{enumerate}
			\end{enumerate}
		\end{enumerate}
	\end{enumerate}

\section{Glossary}
	\begin{enumerate}
		\item All highlighted terms are defined in the Glossary section. 
		\item The Glossary is a binding section of the bylaws. 
		\item Amendments to the Glossary will follow the procedure in \hyperref[bylaw-amendments]{Article I, \autoref*{bylaw-amendments}}.
	\end{enumerate}
	
\section{Appendices}
	\label{appendices}
	\begin{enumerate}
		\item This document will have the following appendices:
			\begin{enumerate}
				\item \gls{ec} Interpretations
					\begin{enumerate}
						\item Will contain a record of \gls{ec} interpretations of the local bylaws.
						\item Interpretations that refer to deprecated parts of the local bylaws may be removed at the discretion of the Vice President.
						\item Items may be added to this appendix by the Vice President.
					\end{enumerate}
				\item Standards Board Precedents
					\begin{enumerate}
						\item Will contain the results of Standards Board Hearings retained for the purpose of establishing precedent.
						\item All parties will remain anonymous.
						\item Items may be added to this appendix by the Arbiter or Parliamentarian of Standards Board and will include the date that the decision was made.
						\item Items that are over five years old may be removed at the discretion of the Arbiter of Standards Board.
					\end{enumerate}
				\item Permanent Legislation
					\begin{enumerate}
						\item Will contain all permanent legislation passed by the chapter.
						\item Upon being passed, permanent legislation will be added to this appendix by the Vice President.
						\item Permanent legislation that is revoked or amended will be removed or changed in this appendix by the Vice President.
					\end{enumerate}
			\end{enumerate}
        \item Appendices to the local bylaws may be amended by the designated officer without the approval of the chapter.
		\item At the end of each semester, the chapter will vote on all amendments to the appendices that were made during that semester.
			\begin{enumerate}
				\item Any amendment that is not approved by the chapter by \gls{simp-maj} will be removed from its appendix.
			\end{enumerate}
	\end{enumerate}
					

\section{Dissolution of the Chapter}
	\begin{enumerate}
		\item Upon the dissolution, abandonment, or discontinuance of this chapter, all the records, rituals, minutes, and correspondence will thereupon become the property of the Grand Chapter of Theta Chi Fraternity.
	\end{enumerate}

