\chapter{Awards}

\section{Award Election Procedure}
	\label{awards-procedure}

	\begin{enumerate}
		\item For each award that the chapter gives:
			
			\begin{enumerate}
				\item Nominations will be opened prior to voting.
				\item Voting
					\label{award-voting}
					\begin{enumerate}
						\item Will take place after nominations have been closed.
						\item Will be done by show of hands.
						\item A brother may vote \emph{No Confidence} if he is not satisfied with any of the nominees.
					\end{enumerate}
				\item There will be no discussion between nominations and voting. \label{award-discussion}
				\item If there are less than 4 nominees, the award will be elected by plurality of voting members present. 
					\begin{enumerate}
						\item Otherwise, there will be a runoff between the three nominees that recieved the highest counts of votes.
					\end{enumerate}
				\item If a plurality of votes cast are \emph{No Confidence}, voting will end and no award will be given.
			\end{enumerate}

	\end{enumerate}

\section{Specified Awards}

	\begin{enumerate}
		\item Brotherhood Award

			\begin{enumerate}
				\item Will be awarded to the brother who best exemplifies the ideals of Theta Chi Fraternity.
				\item Will be awarded before the end of the Spring Semester.
			\end{enumerate}

		\item Alumni Service Award
			\begin{enumerate}
				\item Will be given to the alumnus who has done the most for the currently active chapter.
				\item Will be given annually at OX Roast.
				\item A plaque will be maintained by the OX Roast Chairman that includes the names of the Alumni who have won the award.
			\end{enumerate}

		\item Dream Girl Award
			\label{dream-girl-award}
			
			\begin{enumerate}
				\item Will be bestowed upon the woman associated with Beta Nu Chapter who has done the most for the presently active chapter.
				\item Will be elected by the second regularly scheduled chapter meeting after initiation during the spring semester.
				\item Voting will be done by ballot in direct exception to \hyperref[award-voting]{Article VIII, Section A, \autoref*{award-voting}}.
			\end{enumerate}

		\item Certificate of Appreciation
			
			\begin{enumerate}
				\item May be presented to any person who has demonstrated service of extraordinary care and effort to the chapter.
				\item Will consist of a certificate of appropriate construction and suitable wording which describes the service for which the certificate is being presented.
				\item Any brother eligible to vote may, at any chapter meeting, nominate any person.
				\item Discussion will be allowed for this award in direct exception to \hyperref[award-discussion]{Article VIII, Section A, \autoref*{award-discussion}}.
				\item A nominee must receive a \gls{super-maj} vote to receive this award \hyperref[award-voting]{Article VIII, Section A, \autoref*{award-voting}}.
				\item The chapter may give out any number of this award.
			\end{enumerate}

		\item The chapter may give out any other awards subject to the procedures defined in \hyperref[awards-procedure]{Article VIII, \autoref*{awards-procedure}}.

	\end{enumerate}




