\chapter{Officer Selection and Duties}

\section{Terms of Office}
	\begin{enumerate}
		\item All elected offices will have yearly terms except Standards Board Justice.
			\begin{enumerate}

				\item Each Standards Board Justice will be elected to serve until resignation, ineligibility, removal from office, or graduation (\hyperref[justice-term]{Article XII, Section B, \autoref*{justice-term}}).
			\end{enumerate}
		\item The President will appoint all appointed officers subject to a \gls{simp-maj} vote of the chapter. \label{appointed-approval}
			
		\item Appointed positions will have semesterly terms expect for OX Roast Chair and Critic.
		
		\item The Recruitment Chairman and Public Relations Chairman will serve from the end of the first Rush period after election or appointment through the first Rush period after the election or appointment of a new officer.
	\end{enumerate}

\section{Nominations}
	\begin{enumerate}
		\item Nominations will be opened at least one week before elections.
		\item All members, in order to be eligible for nomination, must be in good standing with the University and the International Fraternity and must not be on \gls{fin-probation}.
	\end{enumerate}


\section{Elections}
	\label{elections}
	\begin{enumerate}
		\item Officers will be elected in accordance with Article V, Section 3 of the \gls{ibl}.
		\item Nominations must be closed in order to elect an officer.
		\item For each position, the election will proceed thusly:
			\begin{enumerate}
				\item For each candidate:
					\begin{enumerate}
						\item Candidates will be allowed speeches following
						these rules:
							\begin{enumerate}
								\item Other candidates will leave the room.
								\item Candidates will be allowed not less than
								three minutes to speak.
							\end{enumerate}
						\item The chapter will be allowed to ask the
						candidate questions following these rules:
							\begin{enumerate}
								\item The chapter will be allowed not less
								than two minutes to question.
								\item Any time not used by a candidate for his
								speech will be allowed for questions.
							\end{enumerate}
					\end{enumerate}
				\item The chapter will discuss the candidates subject to the
				following rules:
					\begin{enumerate}
						\item All candidates will leave the room.
						\item The chapter will be allowed not less than five
						minutes to discuss.
					\end{enumerate}
				\item Candidates will be allowed to vote in the election in direct exception to \hyperref[voting-present]{Article IV, Section A, \autoref*{voting-present}}. 
			\end{enumerate}
    \item Standards Board elections will proceed thusly:
        \begin{enumerate}
            \item There will be one election for all open Standards Board positions.
            \item Each ballot must include a chosen nominee for each opening.
            \item Any nominee receiving a simple majority or plurality of votes is elected to an open position.
            \item If all open positions are not filled, repeat this process.
            \item In the case of electing multiple Standards Board justices, the nominees will be allowed to hear the speeches of the other candidates in exception of Article V, Section 3, Item (a), point i, subpoint A.
        \end{enumerate}
    \item If an elected position should become vacant:
			\begin{enumerate}
				\item The President will appoint an interim officer, preferably a brother who has held the office before.
				\item Nominations for the open position will take place at the next regularly scheduled chapter meeting.
				\item The week following the opening of nominations, elections will proceed as defined above in \hyperref[elections]{Article V, \autoref*{elections}}.
			\end{enumerate}
	\end{enumerate}

\section{Elected Officers and Their Duties}
	\begin{enumerate}
		\item President
			\begin{enumerate}
				\item Performs all duties stated in the \gls{ibl} Article V, Section 6, paragraph a.
				\item Serves as a liaison between the chapter and the community.
				\item Attends all \gls{ifc} and Greek Life Office functions expected of the President.
				\item Responsible for the overall completion of \gls{pytte}.
				\item Serves as a member of \gls{ec}.
				\item Must live in the house.
			\end{enumerate}
		
		\item Vice President
			\begin{enumerate}
				\item Performs all duties stated in the \gls{ibl} Article V, Section 6, paragraph b.
				\item Serves as Parliamentarian for the chapter, Standards Board, and all committees.
				\item Maintains the chapter's local bylaws. %that's these, dear reader!
                \item Records and tracks all legislation passed by the chapter.
				\item Adds all permanent legislation to the appropriate appendix as outlined in \hyperref[appendices]{Article I, \autoref*{appendices}}.
				\item Sits on all committees.
				\item Assigns living space as outlined in \hyperref[housing]{Article VII, \autoref*{housing}}.
				\item Serves as chair of the Bylaw Revision Committee as outlined in \hyperref[bylaw-revisions]{Article IX, \autoref*{bylaw-revisions}}.
				\item Responsible for the Leadership portion of \gls{pytte}.
				\item Serves as chair of \gls{ec} and represents it to the chapter.
				\item Serves as chair of the \gls{ccc}.
				\item May make Ad Hoc Committees at his discretion as defined in \hyperref[adhoccom]{Article V, Section G, \autoref*{adhoccom}}.
				\item Must live in the house.
			\end{enumerate}

		\item Vice President of Health and Safety
			\begin{enumerate}
				\item Performs all duties stated in the \gls{ibl} Article V, Section 6, paragraph c.
				\item Plans and oversees a yearly community outreach event regarding health and safety.
				\item Handles conflict resolution in the chapter with the Chaplain.
				\item Serves as a liaison between the chapter and community health services.
				\item Organizes two semesterly speakers on Health Safety Issues for the chapter.
				\item Maintain relations with the chapter Health and Safety advisor.
				\item Maintains house medical kit.
				\item Maintains a confidential list of pertinent medical issues of brothers for use during chapter emergency.
				\item Responsible for the Citizenship portion of \gls{pytte}.
				\item Serves as a member of \gls{ec}.
				\item Serves on \gls{ccc}.
				\item Serves as chair of the Health and Safety Committee.
				\item Must live in the house.
			\end{enumerate}

		\item Secretary
			\begin{enumerate}
				\item Performs all duties stated in the \gls{ibl} Article V, Section 6, paragraph d.
				\item Records attendance and enforces the standards for attendance in \hyperref[attendance]{Article III, \autoref*{attendance}}.
				\item Serves as Secretary of \gls{ec} 
				\item Collects all legislation, Bylaw amendments, and Officer Reports according to \hyperref[legislation-time]{Article II, \autoref*{legislation-time}} and \hyperref[bylaw-time]{Article I, Section B, \autoref*{bylaw-time}}.
				\item Sets the agenda for chapter meetings according to the \gls{ibl} Article V, Section 8, paragraph d.
				\item Maintains the mailbox and mail closet.
				\item Will create a contact list for the chapter which includes contact information of brothers, advisors, Greek Life, and emergency services.
				\item Maintains the chapter website and the information on it.
				\item Maintains a file server for internal chapter use.
				\item Assists the President in completion of \gls{pytte}.
				\item Serves on \gls{ccc}.
				\item Must live in the house.
			\end{enumerate}

		\item Treasurer \label{treasurer-duties}
			\begin{enumerate}
				\item Performs all duties stated in the \gls{ibl} Article V, Section 6, paragraph e.
				\item Is accountable to the Alumni Corporation.
				\item Collects all fees, dues, assessments, and fines.
				\item Records all transactions made by the chapter.
				\item Will render a written report at the request of any brother. The report will include all monies paid out, all monies received, current bank account balances, and budget updates.
				\item Keeps private all individual account balances except from the brother whose account it is, \gls{ec}, and the Assistant Treasurer.
				\item Issues itemized bills for all brothers and New Members at least three times a semester unless otherwise decided by the chapter.
				\item Announces the names of all members on \gls{fin-probation} at each chapter meeting during the Treasurer's Report or before any vote, whichever occurs first.
				\item Will create a budget following the process outlined in \hyperref[budget]{Article VI, \autoref*{budget}}.
				\item Ensures compliance with the General Rules for chapter finances outlined in \hyperref[fin-rules]{Article VI, \autoref*{fin-rules}}.
				\item Is responsible for all accounts payable.
				\item Will propose a housing contract to the chapter by the last chapter meeting of each semester with a final version to be approved at the first chapter meeting of the next semester.
				\item Will ensure that all brothers living in the house have signed a housing contract by the second chapter meeting of each semester.\label{housing-contract}
				\item Maintains an emergency fund of no less than \$3000 and can withdraw money from the fund only with the authorization of two of the three highest officers. %Example: The chapter is in fucking problems.
				\item Will meet with the Alumni Financial Advisor at least twice each semester.
				\item Will file taxes at least two weeks before the filing deadline each year.
				\item Will ensure that taxes will be reviewed by the financial advisor, alumni housing corporation financial advisor, EC, and the assistant treasurer no later than one month before the filing deadline.
				\item Will send taxes by certified mail, and will distribute this certification to the financial advisor, alumni housing corporation financial advisor, EC, and the assistant treasurer.
				\item Will retain a physical and electronic backup of financial records for no fewer than five years.
				\item Serves as a member of \gls{ec}.
				\item Must live in the house.
			\end{enumerate}
		
		\item Marshal
			\begin{enumerate}
				\item Performs all duties stated in the \gls{ibl} Article V, Section 6, paragraph f.
				\item Will submit a plan as legislation for his office by the first chapter meeting of the semester of his term.
				\item Will reserve a location for Initiation.
                \item Will organize and oversee a member development plan to continue member education beyond initiation.
				\item Responsible for the Ritual portion of \gls{pytte}.
				\item Serves as a member of \gls{ec}.
				\item Must live in the house.
			\end{enumerate}

        \item Recruitment Chairman
			\begin{enumerate}
				\item Performs all duties stated in the \gls{ibl} Article V, Section 6, paragraph l
				\item Assumes responsibility for the direction of the Recruitment Program.
				\item Chairs the Recruitment Committee.
				\item Will run a recruitment workshop each semester.
				\item Will present a Rush calendar to the chapter by Initiation.
				\item Confirms and tracks the attendance of each brother at Rush events (\hyperref[rush-attend-std]{Article XI, Section B, \autoref*{rush-attend-std}}). 
				\item Serves as a member of \gls{ec}. \label{recruit-chair-term}
					\begin{enumerate}
						\item The Recruitment Chairman will serve on \gls{ec} until the end of the Rush period of which he is in charge.
						\item The Recruitment Chairman will not have a vote until the previous semester's chairman is no longer on \gls{ec}.
					\end{enumerate}
                \item Serves on the \gls{ccc}.
                \item Must live in the house.
			\end{enumerate}

		\item Scholarship Chairman \label{schol-chair-duties}
			\begin{enumerate}
				\item Performs all duties stated in the \gls{ibl} Article V, Section 6, paragraph i.
				\item Performs all duties specified by the Greek Life Office, \gls{ifc}, and the University.
				\item Will prepare a written \Gls{schol-program}, submit it to the Office of Greek Life, and pass it as legislation in chapter containing the following:
				\begin{enumerate}
					\item A plan for the creation of Scholarship contracts from Brothers under \gls{academic-watch} or \gls{academic-probation}.
					\item A plan for ensuring the chapter house is an environment conducive to studying.
					\item A plan for providing incentives for academic achievements.
				\end{enumerate}
				\item Works with the Marshal to promote academic well-being among New Members.
                \item Organizes a formal scholarship dinner, preferably with another Greek organization to recognize achievement in scholarship within the chapter.
				\item Will arrange at least one program per semester with an outside speaker who will talk to the chapter about scholarship or an issue relating to scholarship.
				\item Attends monthly meetings with the Greek Community Educational Consultants in accordance with \gls{cwru} Greek Communtiy Standards.
				\item Ensures that member scholarship standards are enforced (\hyperref[member-schol-stds]{Article X, \autoref*{member-schol-stds}}).
				\item Responsible for the Scholarship portion of \gls{pytte}.
                \item Serves on the \gls{ccc}.
                \item Serves on \gls{ec}.
                \item Must live in the house.
			\end{enumerate}
	

		\item Chaplain
			\begin{enumerate}
				\item Performs all duties stated in the \gls{ibl} Article V, Section 6, paragraph g.
				\item Schedules house meals at his discretion.
				\item Handles conflict resolution in the chapter with the VPHS.
				\item Organizes and mediates round table discussions on contentious issues between brothers.
				\item Must live in the house.
			\end{enumerate}

		\item Historian
			\begin{enumerate}
				\item Performs all duties stated in the \gls{ibl} Article V, Section 6, paragraph h.
				\item Sits on the Alumni Relations Committee and assists with the Alumni Database.
				\item Ensures that pictures are taken at chapter events.
				\item Will make an electronic scrapbook for the semester that he serves. A paper copy will be made on a yearly basis in conjugation with the previous historian.
				\item Manages the chapter's online photo and video galleries.
				\item Works with the House Manager to keep composites up to date.
				\item Maintains and updates the photos around the house.
				\item Maintains the chapter museum.
			\end{enumerate}
			
		
		\item First Guard
			\begin{enumerate}
				\item Performs all duties stated in the \gls{ibl} Article V, Section 6, paragraph j.
				\item Plans and executes initiation and prepares the chapter for it.
				\item Serves as Arbiter of Standards Board.
				\item Will enforce reasonable dress in the chapter room as stated in \hyperref[chapter-dress]{Article III, Section D, \autoref*{chapter-dress}}. 
			\end{enumerate}

		\item Second Guard
			\begin{enumerate}
				\item Performs all duties stated in the \gls{ibl} Article V, Section 6, paragraph k.
				\item Serves as Scribe of Standards Board.
			\end{enumerate}
		\item Standards Board Justice
			\begin{enumerate}
				%This is a duplicate of the duties defined in Article 12: Standards Board. If one is changed, the other should be as well.
				\item Hears and rules on all cases brought before Standards Board as defined in \autoref{stds-board}.
				\item Attends all meetings of Standards Board.
				\item Keeps confidential all matters related to judicial proceedings.
				\item Treats all brothers and New Members fairly, impartially, and consistently.
			\end{enumerate}
	

	\end{enumerate}

\section{Appointed Positions}
	\begin{enumerate}
		\item Appointed Positions will include but are not limited to the following:
				\item Critic
					\begin{enumerate}
						\item Will be appointed at each regular meeting.
						\item Will give a report critiquing the chapter at the next regular chapter meeting.
						\item This appointment will not need approval by the chapter in direct exception to \hyperref[appointed-approval]{Article V, Section E, \autoref*{appointed-approval}}.
					\end{enumerate}

                \item Executive Council Member at Large
					\begin{enumerate}
						\item Must have previously served on \gls{ec} for a full term.
						\item Must not hold another \gls{ec} position.
						\item Assists and advises \gls{ec}.
					\end{enumerate}
	
				\item Social Chairman
					\begin{enumerate}
						\item Organizes \glspl{social}.
						\item Ensures that all \glspl{social} run in accordance with all University, Greek Life, \gls{ifc}, \gls{fipg}, and IHQ regulations and policies.
						\item Serves as chairman of the Social Committee (\hyperref[standing-comm]{Article V, Section G, \autoref*{standing-comm}}).
						\item Will attend all \gls{ifc} Social Chairman meetings.
						\item Serves as a member of \gls{ccc}.
					\end{enumerate}

				\item Alumni Relations Chairman
					\begin{enumerate}
						\item Collects materials for and edits the Alumni Newsletter with the help of the Alumni Corporation.
						\item Maintains the alumni database.
						\item Serves as chairman of the Alumni Relations Committee (\hyperref[op-comm]{Article V, Section G, \autoref*{op-comm}}).
						\item Organizes the Alumni Ceremony at the end of the semester in which he serves.
                        \item Sends out Alumni newletter before the last day of classes.
						\item Serves as a member of \gls{ccc}.
					\end{enumerate}

				\item Membership Development Chair
					\begin{enumerate}
						\item  Serves as chairman of the Membership Development Committee.
						\item  Is responsible for creating a Membership Development Plan by the end of his term.
						\item Serves as a member of \gls{ccc}.
					\end{enumerate}

				\item House Manager
					\begin{enumerate}
						\item Will live in the house.
						\item Assumes responsibility for the maintenance of the fraternity residence and surrounding property.
						\item Oversees and assumes responsibility for all property of the fraternity including repair and replacement of equipment.
						\item Provides and maintains an adequate supply of toilet tissue, household cleaning supplies, and maintenance supplies.
						\item Creates, implements, and monitors a parking lot program to be approved as legislation by the chapter.
						\item Distributes house keys to brothers and others on an as needed basis.
					\end{enumerate}

				\item Detail Manager
					\begin{enumerate}
						\item Will pass a house and kitchen detail plan as legislation by the first chapter meeting of the semester in which he serves. The plan must contain provisions for the assessment of fines for delinquency in details.
						\item Assigns weekly house details and weekly kitchen details.
						\item Will be responsible for the direction of all \glspl{work-session}, which may be called at his discretion.
					\end{enumerate}

				\item Philanthropy and Service Chairman
					\begin{enumerate}
						\item Serves on the Health and Safety Committee Committee.
						\item Attends Greek Life Service Chairman meetings.
						\item Ensures that the chapter meets Greek Life goals for philanthropy and service.
						\item Informs the chapter of philanthropy and service opportunities.
						\item Sets individual service requirements for each brother for each semester.
						\item Brings brothers up for standards for not meeting service requirements.
						\item Serves as a member of \gls{ccc}.
					\end{enumerate}
				
				
				\item Public Relations Chairman
					\begin{enumerate}
						\item Serves as chairman of the Public Relations Committee (\hyperref[op-comm]{Article V, Section G, \autoref*{op-comm}}).
						\item Serves on the Recruitment Committee.
						\item Serves on the Social Committee.
						\item Must create a plan for his office by the first chapter meeting of the semester in which he serves and pass it as legislation in chapter.
						\item Serves as a member of \gls{ccc}.
					\end{enumerate}

				\item Risk Manager
					\begin{enumerate}
						\item Performs all duties specified in the \gls{ibl} Article V, Section 6, paragraph l.
						\item Schedules \gls{smarrt} or similar presentations.
						\item Ensures compliance with all Greek Life, University, \gls{ihq}, and \gls{fipg} guidelines and policies.
						\item Attend Office of Greek Life risk manager meetings.
					\end{enumerate}

				\item Interfraternity Congress Representative
					\begin{enumerate}
						\item Represents the chapter at \gls{ifc} meetings.
						\item Must have been a brother for at least one full semester.
					\end{enumerate}
				
				\item Librarian
				\begin{enumerate}
					\item Performs all duties stated in the \gls{ibl} Article V, Section 6, paragraph h.
					\item Sits on the Scholarship Committee.
					\item Manages house library and book collections.
				\end{enumerate}
				
				\item OX Roast Chairman
					\begin{enumerate}
						\item Plans the annual OX Roast event to be held in the fall semester.
						\item Will plan OX Roast to be held during Homecoming Weekend if possible.
						\item The OX Roast Chair will be appointed after OX Roast to serve until the next OX Roast.
					\end{enumerate}

				\item Awards Chairman
					\begin{enumerate}
						\item Leads a committee to fill out Greek Life and \gls{ihq} awards that are due in their term.
						\item Works with the President to fill out Chapter Standards by the fall deadline.
						\item Maintains a system for collecting documentation which includes, but is not limited to the following:
							\begin{enumerate}
								\item All events and activities of the chapter.
								\item Accomplishments of chapter officers (i.e. service hours and recruitment numbers)
							\end{enumerate}
					\end{enumerate}

				\item Greek Week Chairman
					%Informally referred to as the "God Emperor of Greek Week".
					\begin{enumerate}
						\item Organizes the chapter's participation in Greek Week.
						\item Attends Greek Week Chairman meetings sponsored by the Greek Week Steering Committee.
						\item Appoints brothers to captain Greek Week events.
					\end{enumerate}


				\item Food Steward
					\begin{enumerate}
						\item Works with a chef or catering service to maintain a brotherhood meal plan.
						\item Ensures the service chosen for the meal plan is paid for according the agreement with the chef or catering service.
						\item Will work with the Treasurer to determine the cost of the meal plan at least 2 weeks prior to the start of the semester in which the meal plan will run.
						\item Must be on the meal plan.
						\item Works with the Detail Manager to keep public areas in kitchen clean.
						\item Assigns cabinet and fridge space to in-house brothers.
						\item Must live in the house.
					\end{enumerate}

                \item Athletics Chairman
					\begin{enumerate}
						\item Organizes chapter participation in \gls{cwru} intramural activities.
					\end{enumerate}

				\item Temporary Chairmen
					\begin{enumerate}
						\item May be appointed by the President to be in charge of specific events. Examples include DAMAGE Chairman, Formal Chairman, and Master of the Universe.
					\end{enumerate}

	\end{enumerate}

\section{Executive Council}
	\begin{enumerate}
		\item Membership
			\begin{enumerate}
				\item \Gls{ec} will be composed of the following:
					\begin{enumerate}
						\item President
						\item Vice President
						\item Vice President of Health and Safety
						\item Secretary
						\item Treasurer
						\item Marshal
						\item Recruitment Chairman
                        \item Scholarship Chairman
						\item Executive Council Member at Large
					\end{enumerate}
				\item The Recruitment Chairman will serve as in \hyperref[recruit-chair-term]{Article V, Section D, \autoref*{recruit-chair-term}}.

			\end{enumerate}

		\item Purpose, Duties, and Powers
			\begin{enumerate}
				\item Interprets the bylaws as outlined in \hyperref[interpretation]{Article I, \autoref*{interpretation}}. 
				\item Serves as an executive body.
				\item Guides the chapter in emergencies.
				\item Reviews excuses for chapter meetings and other chapter events.
				\item Reviews \glspl{def} (\hyperref[def]{Article VI, \autoref*{def}}). 
				\item Passes Executive Edicts as defined in \hyperref[exec-edict]{Article II, Section D, \autoref*{exec-edict}}
				\item Suspends portions of the Bylaws subject to chapter approval as defined in \hyperref[suspend-bylaws]{Article I, \autoref*{suspend-bylaws}}.
				\item Reviews appeals to \gls{academic-probation} as defined in \hyperref[schol-appeals]{Article X, Section B, \autoref*{schol-appeals}}.
			\end{enumerate}

		\item Voting
			\begin{enumerate}
				\item Voting Members
					\begin{enumerate}
						\item Vice President
						\item Secretary
						\item Treasurer
						\item Marshal
						\item Recruitment Chairman
							\begin{enumerate}
								\item If the previous semester's Recruitment Chairman holds another voting Executive Council position, the current Recruitment Chairman will receive a vote instead.
							\end{enumerate}
                        \item Scholarship Chairman
					\end{enumerate}
				\item Quorum will consist of at least five members, at least four of whom must be voting members.
				\item All votes are decided by an \gls{abs-maj} of \gls{ec}.
                \begin{enumerate}
                    \item The President will have a vote in case of a tie.
                \end{enumerate}
			\end{enumerate}
		\item Procedure
			\begin{enumerate}
				\item \gls{ec} is chaired by the Vice President.
				\item \gls{ec} will meet weekly while school is in session.
				\item \gls{ec} will admit any brother or candidate unless the meeting is declared closed by the President or an \gls{abs-maj} of \gls{ec}.
					\begin{enumerate}
                        \item \gls{ec} may admit any guest by an \gls{abs-maj} vote.
						\item \gls{ec} meetings should be closed to non-\gls{ec} members in situations that require discussing private or emergency matters such as \glspl{def}.
					\end{enumerate}
				\item The Vice President will serve as the representative of \gls{ec} to the chapter.
			\end{enumerate} 
	\end{enumerate}

\section{Committees}
\label{committees}

\begin{enumerate}
	\item Every brother must be a member of at least one Standing and one Operational Committee.
    \begin{enumerate}
        \item If a brother misses three meetings of any one of their assigned committees without obtaining and approved excuse from that committee's chair, that committee's chair may bring that brother up for standards of behavior unbecoming of a brother.
        \item committee meetings scheduled less than five days in advance cannot be counted towards the absences above.
    \end{enumerate}
	\item The chapter will have the following committees:
		\begin{enumerate}	
			\item Standing Committees \label{standing-comm}
				\begin{enumerate}
					\item The Standing Committees of the chapter will include:

						\begin{enumerate}
							\item Recruitment Committee
							\item Public Relations Committee
							\item Health and Safety Committee
							\item Social Committee
						\end{enumerate}
					
					\item All Standing Committees will do the following:
						\begin{enumerate}
							\item Meet at least once every two weeks as directed by their chairman.
							\item Assist the chairman in the discharge of his duties.
							\item Create a set of goals for the committee at the first meeting of the committee.
							\item Work toward the goals of the committee.
						\end{enumerate}
				\end{enumerate}

			\item Operational Committees \label{op-comm}
				\begin{enumerate}	
					\item The Operational Committees of the chapter will include:
					
						\begin{enumerate}
							\item Alumni Relations Committee
							\item Member Development Committee
							\item Scholarship Committee
						\end{enumerate}
					
					\item All Operational Committees will do the following:
						\begin{enumerate}
							\item Meet at least once every month as directed by their chairman.
							\item Assist the chairman in the discharge of his duties.
							\item Create a set of goals for the committee at the first meeting of the committee.
							\item Work toward the goals of the committee.
						\end{enumerate}
				\end{enumerate}

			\item Budget Committee
				\label{budget-committee}
				\begin{enumerate}
					\item Purpose and Duties
						\begin{enumerate}
							\item To create a budget for the chapter for the next year pursuant to \hyperref[budget]{Article VI, \autoref*{budget}}.
							\item To examine any financial issues of the chapter.
						\end{enumerate}

					\item Membership
						\begin{enumerate}
							\item The Treasurer will serve as chairman of the Budget Committee.
							\item The body of the committee will be selected by the treasurer.
						\end{enumerate}

					\item Procedure
						\begin{enumerate}
							\item The committee will be created and convened during the budgeting process outlined in \hyperref[budget]{Article VI, \autoref*{budget}}.
							\item The committee may meet at other times to examine the finances of the chapter at the direction of \gls{ec}.
						\end{enumerate}
				\end{enumerate}

			\item Mandatory Bylaw Revision Committee
				\begin{enumerate}
					\item The Mandatory Bylaw Revision Committee will function in accordance with \hyperref[bylaw-revisions]{Article IX, \autoref*{bylaw-revisions}}.
				\end{enumerate}

					
			\glsreset{ccc}

			\item \gls{ccc}
				\begin{enumerate}
					\item Purpose
						\begin{enumerate}
							\item To facilitate communication between committee chairmen.
							\item To keep the Vice President informed of committee business.
							\item To help the Vice President ensure that committees are performing all necessary duties.
						\end{enumerate}
					\item Membership
						\begin{enumerate}
							\item The Vice President will serve as the Chairman of the \gls{ccc}.
							\item The Chairmen of all Standing and Operational Committees will be members.
							\item Other brothers may be added to the committee at the Vice President's discretion.
						\end{enumerate}
					\item Procedure
						\begin{enumerate}
							\item The committee will meet weekly while school is in session.
							\item The Vice President will evaluate progress toward committee goals.
						\end{enumerate}	
				\end{enumerate}

		\end{enumerate}

	\item Ad Hoc Committees
		\begin{enumerate}
			\item The Vice President has the power to make other committees at his discretion. \label{adhoccom}
		\end{enumerate}
\end{enumerate}

							

