\chapter{Standards Rulings}
\begin{enumerate}
	\item Date: September 25, 2010\\Charges: A brother was under a 2.2 GPA for two consecutive semesters.\\Plea: Responsible.\\Sanctions: Recommendation for suspension, voting privileges suspended until off of academic probation.
	\item September 25, 2010\\Charges: A brother was under a 2.2 GPA for two consecutive semesters. Brother was currently on co-op.\\Plea: No Contest.\\Sanctions: Recommendation for suspension, voting privileges revoked upon return from co-op.
	\item October 22, 2010\\Charges: A brother was living outside of the house without permission from the chapter.\\Plea: No Contest.\\Sanctions: Formal apology in chapter, \gls{staggard} for time equal to time out of the house upon return to the house. Recommendation for suspension.
	\item February 7, 2012\\Charges: A brother was brought up for conduct unbecoming.\\Plea: Not Responsible.\\Sanctions: Letter of formal apology to those offended, immediate removal from office of Standards Board Justice.
	\item January 11, 2015\\Charges: A brother was living outside of the house without permission from the chapter.\\Plea: No Contest.\\Sanctions: The brother must pay the difference between cost to live in the house and his rent, loss of voting rights, and required to still do house and kitchen details.
	\item March 21, 2015\\Charges: Four brothers were planning to live outside of the house without permission from the chapter\\Plea: No Contest\\Sanctions: The brothers must remain on the house detail plan, maintain contact with the Scholarship Chair, and their voting rights were revoked.
	\item April 26, 2015\\Charges: A brother was planning to live outside of the house without permission from the chapter\\Plea: No Contest\\Sanctions: The brother must complete kitchen details or actively attend study tables at a rate set by the Scholarship Chair.
	\item February 28, 2016\\Charges: A brother was planning on living outside the house without the permission of the chapter\\Plea: Not Responsible\\Sanctions: No repercussions
\end{enumerate}
